Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-03-04 supplement.tex
cleanup small comments

Finally, we estimated uncertainty due to the finite amount of genetic material
used in inference using bootstrap over 500 segments along the genome with
roughly equal lengths of retained sequences within each segment. First, for
each distance bin, we used these bootstrap samples to obtain a
variance-covariances matrix across all statistics. This variance-covariance
matrix was used to obtain a model likelihood for each recombination distance
bin and single-locus nucleotide diversity, as a multivariate Gaussian
likelihood. The full model likelihood was taken as the product of likelihoods
over each bin. In other words, we optimized a composite likelihood where
observations in different bins were taken to be independent. To account for
correlations across bins in uncertainty estimates, we estimated parameter
confidence intervals using the same bootstrap set using the Godambe information
matrix \citep{Coffman2016-yq}. \sgcomment{is redundancy here with section
"Optimization using moments". I think we can get rid of this and say:
"optimization and uncertainty calculations are described in section
"Optimization using moments""?, This may be a bit more complicated, since the
Optimizatino section relies on this description. I think we should just punt
the bootstrap description to that section. TODO: discuss Aaron + Simon}

@@

\subsection{Confidence intervals using Godambe methods}

The bootstrap replicates that were used to compute the variance-covariance
structure of the observed statistics within bins were also used to build 500
bootstrap replicates of the data by resampling with replacement. For the best
fit parameters, we computed confidence intervals using the Godambe Information
approach, which corrects composite likelihood estimates of confidence intervals
to account for nonindependence in the data, including linkages between loci and
nonindependence of recombination bins \cite{Coffman2016-yq}.

>>>>

@@

\subsection{Uncertainty and confidence intervals using Godambe methods}

To compute likelihoods, we needed an estimate of the joint distribution of summary statistics. 
We estimated uncertainty due to the finite amount of genetic material
used in inference using bootstrap over 500 segments along the genome with
roughly equal lengths of retained sequences within each segment. First, for
each distance bin, we used these bootstrap samples to obtain a
variance-covariances matrix across all statistics. This variance-covariance
matrix was used to obtain a model likelihood for each recombination distance
bin and single-locus nucleotide diversity, as a multivariate Gaussian
likelihood. The full model likelihood was taken as the product of likelihoods
over each bin. In other words, we optimized a composite likelihood where
observations in different bins were taken to be independent.

For the best fit parameters, we computed confidence intervals using the 
same set of bootstraped samples and Godambe Information
approach \citep{Coffman2016-yq}, which corrects composite likelihood estimates of confidence intervals
to account for nonindependence in the data, including linkage between loci and
nonindependence of recombination bins.
